Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-03 doc/LinksToDAG.tex
everything
makefile now creates body.pdf and supplement.zip minor edits

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took 1.5 hours. \noteJH{A run of 10,000 sentences takes 3142 seconds (update in final version!)}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, \input{figure/allowed_labels_both.tex}of \input{figure/allowed_labels_total.tex}link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = \input{figure/label_token_disallowed}$ of \input{figure/label_token_total}link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded}of the English sentences and 0.15\% of the Russian sentences had at least one multiheaded word.
\noteJE{2 significant digits is enough}
\noteJE{update these numbers}

@@

Recall that \url{http://www.abisource.com/projects/link-grammar/dict/summarize-links.html} documents the 122 link types in the English link grammar lexicon.  Below is the result of our largest English run, whose corpus uses !!! of these types.

@@

% Uncomment this to add in all of the parses. Warning: compilation will take a long time.
%\input{figure/parses.tikz}

>>>>

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took 1.5 hours. \noteJH{A run of 10,000 sentences takes 3142 seconds (update in final version!)}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, only \input{figure/allowed_labels_both.tex}of \input{figure/allowed_labels_total.tex}link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = \input{figure/label_token_disallowed}$ of \input{figure/label_token_total}link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded}of the English sentences but (disappointingly) only 0.15\% of the Russian sentences had at least one multiheaded word.
\noteJE{2 significant digits is enough}
\noteJE{update these numbers}

@@

Recall that \url{http://www.abisource.com/projects/link-grammar/dict/summarize-links.html} documents the 122 link types in the English link grammar lexicon.  Below is the result of our largest English run, whose corpus uses 107 of these types. \noteJH{automatically generate this number}

@@

% Uncomment this to add in all of the parses. Warning: compilation will take a long time.
\input{figure/parses.tikz}
